### 2011-07-02 Paper/Paper.tex
Fiddling with tied notes, draft performance and score features implemented
Started on HMM featureextraction on mozart may not work

\begin{abstract}
This paper introduces a system for expressively performing transcribed music (scores) using statistical learning from a dataset. The dataset that is used contains performances aligned to the corresponding score. Expression is considered to be the way in which the performance deviates from the score. Expressive actions are predicted from links found between musical structure and expression. Previous expressive actions are also incorporated in the predictions. Musical structure will be automatically extracted from the scores using a set of formal rules that assign a hierarchical grouping structure to the music. To system will be able to deal with polyphonic music by splitting the scores into melody and harmony.

@@

\section{Method}
\section{Evaluation and Results}
\subsection{Subjective Listening}
\subsection{Correlation}
\section{Conclusion}
\section{Future Work}

>>>>

\begin{abstract}
In this paper a system will be presented that will learn 
This paper introduces a system for expressively performing transcribed music (scores) using statistical learning from a dataset. The dataset that is used contains performances aligned to the corresponding score. Expression is considered to be the way in which the performance deviates from the score. Expressive actions are predicted from links found between musical structure and expression. Previous expressive actions are also incorporated in the predictions. Musical structure will be automatically extracted from the scores using a set of formal rules that assign a hierarchical grouping structure to the music. To system will be able to deal with polyphonic music by splitting the scores into melody and harmony.

@@

\section{Method}
\section{Evaluation and Results}
\subsection{Subjective Listening}
\subsection{Correlation}
\section{Conclusion}
\cite{markwin}
\section{Future Work}
